Download data

### 2025-09-30 README.qmd
Adding scripts, files, and manuscript :fire:

---
format: gfm
---

@@

```{r setup, include=FALSE}
library(emoji)
```

## Procrastination as a Marker of Cognitive Decline: Evidence from Longitudinal Transitions in the Older Adult Population

@@

##  `r emoji_glue(":potato::spiral_shell:")`: Note on "crisp clam" project name

>>>>

---
title: "Procrastination as a Marker of Cognitive Decline: Evidence from Longitudinal Transitions in the Older Adult Population"
format: gfm
---

@@

```{r setup, include=FALSE}
library(emoji)

yaml_metadata <- rmarkdown::yaml_front_matter(here::here("manuscript", "manuscript.qmd"))

title <- yaml_metadata$title
abstract <- yaml_metadata$abstract

emoji_out <- emoji_glue(":potato::spiral_shell:")
```

::: {.content-visible when-format="markdown"}

---

@@

---

:::

---

> Monaghan, C., de Andrade Moral, R, Kelly, M, & McHugh Power, J. "`r title`".

---

## Abstract

`r abstract`

## `r emoji_out`: Note on "crisp clam" project name

### 2025-09-30 analysis/data-exploration.qmd
Adding scripts, files, and manuscript :fire:

# Setting up

@@

theme_set(
  theme_minimal() +
    theme(
      plot.title = element_text(
        hjust = 0.5,
        size = 14,
        face = "bold",
        colour = colour
      ),
      plot.subtitle = element_text(
        hjust = 0.5,
        size = 10,
        colour = colour
      ),
      axis.title = element_text(
        size = 10,
        face = "bold",
        colour = colour
      ),
      strip.text = element_text(
        size = 10,
        face = "bold",
        colour = colour
      ),
      panel.grid = element_blank(),
    )
)
```

## Reading in data

```{r}
#| label: data

data <- read.csv(here::here("analysis/data/data.csv")) 
```

# Dementia Dataset

@@

```{r}
#| fig-width: 8
#| code-fold: true
#| code-summary: "Check out my code"
#| label: fig-missing-data
#| fig-cap: Occurance of missing data across HRS waves (participants were gathered from the 2020 HRS wave [in red])
#| warning: false

@@

data |>
  select(any_of(paste0("cogtot27_imp", 1996:2022))) |>
  rename_with(~ str_replace(., "cogtot27_imp", ""), starts_with("cogtot27")) |>
  visdat::vis_dat() +
  labs(title = "Missing data across HRS Waves (1996 - 2022)", 
       subtitle = "Total Cognitive Scores") +
  theme(
    plot.title = element_text(
      hjust = 0.5, size = 14, face = "bold", colour = colour),
    plot.subtitle = element_text(
      hjust = 0.5, size = 12, face = "bold", colour = colour),
    panel.grid = element_blank(),
    axis.text.x = element_text(size = 9, colour = colours),
    legend.position = "none"
  )

>>>>

@@

theme_clean <- function() {
  theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5, size = 14, face = "bold", colour = colour ),
      plot.subtitle = element_text( hjust = 0.5, size = 10, colour = colour),
      axis.title = element_text(size = 10,face = "bold",colour = colour),
      strip.text = element_text(size = 10,face = "bold",colour = colour),
      panel.grid = element_blank(),
    )
  }

# Read in data -----------------------------------------------------------------
data <- read.csv(here::here("analysis/data/data.csv")) 
```

@@

```{r}
#| label: fig-missing-data
#| code-fold: true
#| code-summary: "Check out my code"
#| fig-width: 8
#| fig-cap: Occurance of missing data across HRS waves (participants were gathered from the 2020 HRS wave [in red])
#| warning: false

@@

data |>
  select(any_of(paste0("cogtot27_imp", 1996:2022))) |>
  rename_with(~ str_replace(., "cogtot27_imp", ""), starts_with("cogtot27")) |>
  visdat::vis_dat() +
  labs(title = "Missing data across HRS Waves (1996 - 2022)", 
       subtitle = "Total Cognitive Scores") +
  theme_clean() +
  theme(legend.position = "none")

### 2025-09-30 analysis/data-final.qmd
Adding scripts, files, and manuscript :fire:

---
title: "Download final data"
format:
  html:
    code-tools: false
    toc: false
---

@@

## Data

@@

>>>>

---
title: "Download data"
format:
  html:
    code-tools: false
    toc: false
---

@@

## Data (wide format)

@@

## Data (long format)

<a class="btn btn-primary btn-sm" target="_blank" href="data/data_long.csv">{{< fa table >}} &ensp;<span class="font-monospace">data.csv</span></a> &emsp; <a class="btn btn-success btn-sm" target="_blank" href="data/data_long.rds">{{< fa brands r-project >}} &ensp;<span class="font-monospace">data.rds</span></a> &emsp; <a class="btn btn-warning btn-sm" target="_blank" href="data/data_long.dta">{{< fa table-cells >}} &ensp;<span class="font-monospace">data.dta</span></a>
